The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
edit fitness P5

Social scale is another major consideration for social network analysis, especially in the context of different types of interactions and associations in the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015). It is a common trope that individuals must be associating to interact and most studies therefore assume that proximity is proxy for interacting (Farine, 2015). For instance, baboons need to be in proximity in order to groom each other, but this trope highlights human bias toward interactions that can be readily observed in the field. Animals have certain interactions that do not require proximity such as long-distance vocalization and olfactory signals (Carter et al., 2015). With the advancement of bio-logging technology, our ability to record social interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017). The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good a social proximity is for various forms of interacting in a holistic way.

These different social scales can have different fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) that had stronger, more stable associates and grooming partners but not more partners in general had greater survivorship than those who did not (Ellis, Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019). This finding highlights the need to look at social network positions at both multiple temporal and social scales to understand the social positions and fitness repercussions of individuals, and multilayer networks provide an avenue to do so considering the whole social system rather than just one type of social interaction at a time, which is what has been done under most circumstances but is not very realistic.

>>>>

Social scale is another major consideration for social network analysis, especially in the context of different types of interactions and associations in the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015). It is a common trope that individuals must be associating to interact and most studies therefore assume that proximity is proxy for interacting (Farine, 2015). For instance, baboons need to be in proximity in order to groom each other, but this trope highlights human bias toward interactions that can be readily observed in the field. Animals have certain interactions that do not require proximity such as long-distance vocalization and olfactory signals (Carter et al., 2015). With the advancement of bio-logging technology, our ability to record social interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017). The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good a social proximity as a proxy for social interactions in a holistic way.

These different social scales can have different fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) that had stronger, more stable social associates and grooming partners, but not more social partners, had higher survivorship than those who did not (Ellis, Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019). This finding highlights the need to investigate the effect of temporal and social scales on the relationship between social network positions and fitness. Multilayer networks provide an avenue to do so considering the whole social system rather than just one type of social interaction at a time, which is what has been done under most circumstances but is not very realistic.
